%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Ravichandran Rajappa} \\[7.5pt]
\href{https://github.com/r2vichan}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://linkedin.com/in/ravi-rajappa}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:rrajapp1@asu.edu}{\raisebox{-0.05\height}\faEnvelope \ rrajapp1@asu.edu} \ $|$ \ 
\href{tel:+1 (602) 566-1887}{\raisebox{-0.05\height}\faMobile \ +1 (602) 566-1887} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2023 - present & Master of Science in Computer Science at \textbf{Arizona State University} \hfill \normalsize (GPA: 4.0/4.0) \\

2016 - 2020 & Bachelor's Degree at \textbf{Visvesvaraya Technological University} \hfill (GPA: 7.29) \\ 
\end{tabularx}


%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
% \section{Summary}
% This CV is automatically generated and deployed using the \href{https://github.com/jitinnair1/autoCV}{autoCV} template along with GitHub Actions such that a new version of the CV is compiled, published and ready for use when the cv.tex file is updated. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.

%Experience
\section{Work Experience}

\begin{jobshort}{Software Engineer - Identity Access Management}{Oct 2020 - Jul 2023}
Achievements:
• Developed solutions to modernize and automate internal Identity management processes, including migration, development, and testing while collaborating with technical leads and various teams within the IAM space.
• Implemented: A modern automation framework built on Amazon Web Services (AWS) and Node.js, driving a transition away from legacy on-premise PowerShell setup, resulting in an 85\% reduction in Privileged Access Management (PAM) service execution time and a 60\% reduction in lines of code.
• Architected: The infrastructure for a housekeeping portal to centralize all internal identity management processes, including applications and processes critical to Quarterly Access Reviews.
• Spearheaded: deployment of a micro-service using AWS Lambda and Node.js to manage extraction, processing and deletion or storage of over 16,500 decommissioned accounts from internal CyberArk environment databases, aligning with SOX compliance and audit requirements. Led a team in leveraging Git for version control while employing CI/CD best practices for deployment automation.
• Achieved: the AWS Certified Developer – Associate and CyberArk Trustee certifications, demonstrating mastery of core AWS services, adherence to architecture best practices, and proficiency in development and deployment tools and an understanding of privileged account access management and its critical role in navigating threat landscapes.
\end{jobshort}


\begin{joblong}{Spring Intern - Technology Consultant}{Jan 2020 - Jul 2020}
• Implemented: proprietary servers built in-house and ensured high availability of these servers, overseeing deployment, documentation, testing, and support, to improve operational efficiency by 20\%.
• Deployed: Servers by employing the VMWare ESXi suite, partnering with various teams, and ensuring high uptime commitment for enterprise, with 99.99999\% availability.
• Initiated: and executed design and development of an enterprise SharePoint page, utilizing HTML and CSS to transform enterprise news communication, simplifying maintenance and elevating user engagement.
• Directed: a team in an overhaul of technical training materials, managing development and digitization efforts and achieving an enterprise-scale reduction in manual processes and over 3,500 training material documents.
• Conducted: a highly engaging workshop on content digitization basics and best practices, skillfully mentoring and communicating concepts to over 100 employees, resulting in strategic identification of key areas for improvement.
\end{joblong}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Face Mask Detector} & \hfill \href{https://some-link.com}{Link to Demo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{• Worked closely with a team to design a face mask detection app for webcam video, harnessing PyTorch neural
networks, achieving 96\% training and 93\% testing accuracy by researching trends, and leveraging datasets for face-mask
images amid the COVID-19 pandemic.
• Led development of a pipeline to streamline code update and review processes, enabling team members to perform and
implement changes more efficiently and fostering a collaborative project environment.}  \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Some Skills &  \normalsize{This, That, Some of this and that etc.}\\
Some More Skills  &  \normalsize{Also some more of this, Some more that, And some of this and that etc.}\\  
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
